---
output:
  github_document:
    html_preview: false
---
[![Travis build status](https://travis-ci.org/marcosci/landscapetools.svg?branch=master)](https://travis-ci.org/marcosci/landscapetools)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/marcosci/landscapetools?branch=master&svg=true)](https://ci.appveyor.com/project/marcosci/landscapetools)
  [![Coverage status](https://codecov.io/gh/marcosci/landscapetools/branch/master/graph/badge.svg)](https://codecov.io/github/marcosci/landscapetools?branch=master)
  
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# landscapetools

`landscapetools` provides utility functions to work with landscape data (raster* 
Objects). 


### The following functions are implemented:

#### Themes:

`theme_nlm`, `theme_nlm_grey`: Opinionated ggplot2 theme to visualize raster (continous data).<br/>
`theme_nlm_discrete`,`theme_nlm_grey_discrete`: Opinionated ggplot2 theme to visualize raster (discrete data).<br/>
`util_import_roboto_condensed`: Import Roboto Condensed font for `theme_nlm`.<br/>

#### Utilities:

`util_binarize`: Binarize continuous raster values, if > 1 breaks are given return a RasterBrick.<br/>
`util_classify`:  Classify a raster into proportions based upon a vector of class weightings.<br/>
`util_merge`: Merge a primary raster with other rasters weighted by scaling factors.<br/>
`util_raster2tibble`, `util_tibble2raster`: Coerce raster* objects to tibbles and vice versa.<br/>
`util_rescale`: Linearly rescale element values in a raster to a range between 0 and 1.<br/>

#### Visualization

`util_plot`: Plot a Raster* object with the landscapetools default theme (as ggplot).<br/>
`util_facetplot`: Plot multiple raster (RasterStack, -brick or list of raster) side by side as facets.<br/>


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marcosci/landscapetools")
```

## Usage

```{r fig.retina=2}
library(patchwork)
library(nlmr)
library(landscapetools)
library(ggplot2)
# Create artificial landscape
nlm_raster <- nlm_mpd(ncol = 200, nrow = 200, roughness = 0.8)
```


### Utilities

### Binarize
```{r fig.retina=2}
binary_stack <- util_binarize(nlm_raster, breaks = c(0.3, 0.5, 0.7, 0.9))
util_facetplot(binary_stack)
```
### Classify
```{r fig.retina=2}
classified_raster <- util_classify(nlm_raster,
                                   c(0.5, 0.25, 0.25),
                                   level_names = c("Land Use 1", "Land Use 2", "Land Use 3"))
util_plot(classified_raster, discrete = TRUE)
```

### Merge
```{r fig.retina=2}
pL <- nlm_edgegradient(ncol = 100,
                       nrow = 100)

sL1 <- nlm_distancegradient(ncol = 100,
                            nrow = 100,
                            origin = c(10, 10, 10, 10))
sL2 <- nlm_random(ncol = 100,
                  nrow = 100)
mL1 <- util_merge(pL,
                  c(sL1, sL2),
                  scalingfactor = 1)
  
util_plot(mL1)
```
### Visualization
```{r fig.retina=2}
g1 <- util_plot(nlm_raster) + guides(fill = FALSE)
g2 <- util_plot_grey(nlm_raster) + guides(fill = FALSE)
g1 + g2
```

## Meta

* Please [report any issues or bugs](https://github.com/marcosci/landscapetools/issues/new/).
* License: GPL3
* Get citation information for `landscapetools` in R doing `citation(package = 'landscapetools')`
* We are very open to contributions - if you are interested check [Contributor Code of Conduct](CONTRIBUTING.md).
    * Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
