---
output: github_document
---
[![Travis build status](https://travis-ci.org/marcosci/landscapetools.svg?branch=master)](https://travis-ci.org/marcosci/landscapetools)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/marcosci/landscapetools?branch=master&svg=true)](https://ci.appveyor.com/project/marcosci/landscapetools)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# landscapetools

The goal of landscapetools is to ...

## Installation

You can install the released version of landscapetools from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("landscapetools")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marcosci/landscapetools")
```

## Meta

* Please [report any issues or bugs](https://github.com/marcosci/landscapetools/issues/new/).
* License: GPL3
* Get citation information for `landscapetools` in R doing `citation(package = 'landscapetools')`
* We are very open to contributions - if you are interested check [Contributor Code of Conduct](CONTRIBUTING.md).
    * Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
   
## Dependencies

`landscapetools` imports many great packages that it depends on. Many thanks to the developers of these tools:

```{r, echo  = FALSE, result = "asis", comment = ""}
desc = read.dcf("DESCRIPTION")
headings = dimnames(desc)[[2]]
fields = which(headings %in% c("Depends", "Imports"))
pkgs = paste(desc[fields], collapse = ", ")
pkgs = gsub("\n", " ", pkgs)
strsplit(pkgs, ",")[[1]]
```
